---
title: "Assignment 1"
author: "Aarush Bhardwaj"
date: "01/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# For this assignment we will be using the built-in dataset-iris
# importing iris
```{r datasets}
library(datasets)
```


# Print descriptive stats for a selection of variables
```{r}
summary(iris)
```

# Transforming the Species column from a column that has names of species
# into a column that contains the numbers (0-2) for each species
# while keeping the class of the column unchanged.

# Copying iris data into data1 dataframe.
```{r iris}
data1 <- data.frame(iris)
summary(data1)
```

# Changing the species column by assigning setosa a class label - 0.
```{r}
data1$Species <- as.character(data1$Species)
data1[data1 == "setosa"] <- "0"
data1$Species <- as.factor(data1$Species)
```

# Changing the species column by assigning versicolor a class label - 1.
```{r}
data1$Species <- as.character(data1$Species)
data1[data1 == "versicolor"] <- "1"
data1$Species <- as.factor(data1$Species)
```

# Changing the species column by assigning virginica a class label - 2.
```{r}
data1$Species <- as.character(data1$Species)
data1[data1 == "virginica"] <- "2"
data1$Species <- as.factor(data1$Species)
```
# The above step will help us greatly when we feed this data
# to a machine learning model. The Species label will be our target.
```{r}
summary(data1)
```

# Plotting Quantitative Variable Petal.Length
# Here we are using the iris dataset but
# we can also use the data1 dataframe
```{r echo=FALSE}
plot(data1$Petal.Length)
```
# Plotting Petal.Length and Sepal.Length
```{r echo=FALSE}
plot(data1$Petal.Length, data1$Sepal.Length)
```
